Brundle Development

### 2017-12-05 Manuscript_Figures.Rmd
Reanalysis of H4K12ac data
Output for GEO

```{r,results='hide', message=FALSE, warning=FALSE}
filename<-"Rdata/066_SLX-15090_dba_human_ER_CTCF.rda"
load(filename)

@@

@@

>>>>

```{r,results='hide', message=FALSE, warning=FALSE}
filename<-"Rdata/066_SLX-15090_dba_human_ER_CTCF_merged.rda"
load(filename)

@@

write.csv(dba.report(jg.dba_analysis,th=1),file="csv/H4_normalised_results.csv")

@@

write.csv(dba.report(jg.dba_analysis,th=1),file="csv/E2_normalised_results.csv")
